Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-11 paper/reviewers-response.Rmd

> L27: unclear what "its" refers  to

We now explicitly state "species' degree" \lr{R2-species-degree}

> L111, 114: "are comprised of" should be "comprised "

> "*L343*: I am not sure about citing Table 2 for the first time in the Discussion. Might it be more useful to cite this in the Introduction?""

We now introduce the glossary at the end of the introdyction on \lr{M-R2-ref-glossary}.

@@

> "I'd like to commend the authors to this revised version of the manuscript on "Keystoneness, centrality, and the structural controllability of ecological networks". I thoroughly enjoyed the re-written manuscript, which is now considerably more accessible and clearly targets the community of network ecologists, while not ignoring the importance of the applied relevance of the findings. Overall, I don't have any major comments. I guess the language is in parts on the casual side, yet without compromising the preciseness or clarity of the text. I noticed a few typos or style errors that the authors may want to address"

We are pleased that the reviewer "thoroughly enjoyed the re-written manuscript", and appreciate the identified issues. We have addressed all issues in the text and identify these in red.

> A few references require editing to journal style (e.g. remove initials for many citations)

We have corrected all of them except on \lr{R2-citation-with-name} where the initial is used to distinguis between two authors with the same last name

### 2019-01-11 paper/reviewers-response.Rmd

# Associate Editor's comments:

> "I think this ms now makes much clearer the potential insights to be gained by applying control theory to interaction networks. In particular, the authors have done a nice job of explaining how their findings reinforce existing ideas in the literature on the stability of ecological networks while also acknowledging limitations. The reviewers identify a few remaining issues that should be straightforward to address. I also noticed a few issues"

Thank you for the positive feedback. We have addressed all of the specific issues raised and highlight these in red text in our resubmitted manuscript.

> "*L9*: I think here and throughout much of the text, species should be possessive when followed by a noun ("species role" should be "species' role"). The possessive is currently used in some instances but is inconsistently applied throughout the ms."

*Accepted and changed*. We have checked through the manuscript and corrected this where relevant. Besides *specie's role*, we also changes instances of *species' contribution*, *species' degree*, *species' control capacity*, among others.

> "*L25*: 'every invasive species in our dataset was part of it' Here it was unclear what 'it' refers to (the set of critical species), and the reference to a singular dataset when you have 20 networks in total was a bit confusing to me.

*Accepted and changed*. We have made this clearer as follows: "and included every invasive species in our dataset" (\lr{M-R2-our-dataset})

> "*L23-26*: in these lines, you refer to critical species, but I think the distinction between having high control capacity versus being critical needs to be defined (briefly) earlier (it is stated in *L18-19* that you will quantify both control capacity and identify critical species, but it is not explained how they are distinct)."

*Accepted and changed*. We now identify the distinction between high control capacity and being critical on \lr{M-R2-define-control-capacity}. The text now reads "It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity."

> "*L27*: unclear what 'its' refers  to."

*Accepted and changed*. We now explicitly state "species' degree" in  \lr{M-R2-species-degree}

> "*L234, 235*: awkward to refer to species as 'they' and 'their'"

*Accepted and changed*. We have changed this to "it" and "its"

> "*L296*: 'More details in Supporting Information.' is a sentence fragment."

*Accepted and changed*. We have corrected this on \lr{M-R2-sentence-fragment}. The text now reads "See Supporting Information Section \@ref(S-visitation-as-proxy) for more details".

@@

> "*L343*: I am not sure about citing Table 2 for the first time in the Discussion. Might it be more useful to cite this in the Introduction?""

We now introduce the glossary at the end of the introdyction on \lr{M-R2-ref-glossary}.

> "*L111, 114*: 'are comprised of' should be 'comprised'. *L339, 432*: 'at' should be 'in'. *L341*: 'allow' should be 'allowed'. *L355*: missing period."

*Accepted and changed*. Thank you for pointing out these mistakes, we corrected all of them.

### 2019-01-11 paper/manuscript.Rmd
Moving glossary to the intro
Comments to associate editor done
Close #56

2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical—have maximum control capacity—in this context. 
We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.

>>>>

2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity. 
We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.
